opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-12-22 chapters/04_our_dataset.tex
Added alphabetic labeling rule in Usage section

%TODO: A paragraph on how data is correlated
The degree of variation between the patterns is different for each contribution. For example, the CRNS and the INT contributions each are collections that encompass many research projects over a large period of time and hence exhibit a high degree of variability between individual patterns. In contrast, the contributions by the USC and the LBNL contain many very similar patterns. The patterns in the USC datasets are similar because the underlying samples are all variations of \ce{CuNi} and \ce{CuAl} alloys collected on the same machine. The patterns submitted by the LBNL are similar because they stem from in-situ recordings where several hundred or several thousand patterns were collected over time per sample while they were undergoing physical processes. 
\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.85\linewidth]{figures/hist.png}
    \caption{Histograms detailing the distribution of properties in the opXRD dataset: a) distribution of spacegroups present in labeled data; b) distribution of angular resolution in all data; c) distribution of smallest and largest recorded $2\theta$ values for all data.}
    \label{fig:histograms}
\end{figure}

@@

Data was collected from two separate studies. A first study focused on metal-halide perovskite precursor solutions. For this study, two datasets were collected. The first dataset was collected from spin-coating triple-cation metal-halide perovskite precursor solutions with the composition \ce{Cs}$_{0.05}$(MA$_{0.23}$FA$_{0.77}$)\ce{Pb}$_{1.1}$(\ce{I}$_{0.77}$\ce{Br}$_{0.23}$)$_{3}$ onto various substrates. Here, MA stands for Methylammonium and FA stands for Formamidinium. The substrates onto which these solutions were coated include glass, which is amorphous, and $\ce{GaAs}$ wafers, which are single crystalline. Other substrates were stacks of glass/indium tin oxide, stacks of \ce{GaAs}/CIGS, and stacks of glass/CIGS. Here, CIGS stands for a stack of \ce{Mo}, \ce{Cu}(\ce{In}, \ce{Ga})\ce{Se2},\ce{Cds} and \ce{ZnO}. Some of the substrates were additionally covered with a self-assembling monolayer of MeO-2PACz. The $\ce{GaAs}$ substrates were prepared by Dr. Jiro Nishinaga from the National Institute of Advanced Industrial Science and Technology (AIST) in Japan and the glass/CIGS substrates by Dr. Christian Kaufmann and his team at Helmholtz-Zentrum Berlin (HZB) in Germany. Data collection was performed in situ during thin-film deposition using a custom-made spin-coating and annealing stage. \\

@@

For this study, experimental XRD data were collected at beamline 12.3.2 of the Advanced Light Source, the synchrotron at Lawrence Berkeley National Laboratory. The data were collected using a photon energy of 10 $\si{keV}$ ($\lambda = 1.23984 \text{\AA}$), selected using a Si(111) monochromator. Measurements were taken in grazing incidence geometry, i.e. using a beam incidence angle of $1\degree$. Two-dimensional diffraction images were recorded using a Dectris Pilatus 1M area detector at an angle between $34\degree$ and $36\degree$ with a sample-to-detector distance of roughly $190 \ \si{mm}$. The two-dimensional data were calibrated using an Al$_{2}$O$_{3}$ calibration standard and integrated along the azimuthal angle. \\

@@

In a second study, the phase evolution of the Mn-Sb-O system varying with annealing temperature was measured. The temperatures used to analyze the crystal structure of the Mn-Sb-O system were chosen depending on the number of phase transitions appearing for a certain temperature range. Few changes in the crystal structure appear between room temperature and 300$\degree$C and phase transitions appeared from 300$\degree$C until 850$\degree$C. No phase transition appeared when cooling down. Therefore, the crystal structure was measured every 100$\degree$C between room temperature and 300$\degree$C; every 50$\degree$C between 300$\degree$C and 850$\degree$C; and every 200$\degree$C when cooling down. The heating and cooling rates are fixed for all the experiments at 50$\degree$C/min and the holding time is fixed at 2 min. \\

>>>>

%TODO: A paragraph on how data is correlated
The degree of variation between the patterns is different for each contribution. For example, the CRNS and the INT contributions each are collections that encompass many research projects over a large period of time and hence exhibit a high degree of variability between individual patterns. In contrast, the contributions by the USC and the LBNL contain many very similar patterns. The patterns in the USC datasets are similar because the underlying samples are all variations of \ce{CuNi} and \ce{CuAl} alloys collected on the same machine. The patterns submitted by the LBNL are similar because they stem from in-situ recordings where several hundred or several thousand patterns were collected over time per sample while they were undergoing physical processes. 
\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\linewidth]{figures/hist.png}
    \caption{Histograms detailing the distribution of properties in the opXRD dataset: a) distribution of spacegroups present in labeled data; b) distribution of angular resolution in all data; c) distribution of smallest and largest recorded $2\theta$ values for all data.}
    \label{fig:histograms}
\end{figure}

\pagebreak

@@

In total three different datasets were collected. The first and second datasets focused on metal-halide perovskite precursor solutions. The first dataset was collected from spin-coating triple-cation metal-halide perovskite precursor solutions with the composition \ce{Cs}$_{0.05}$(MA$_{0.23}$FA$_{0.77}$)\ce{Pb}$_{1.1}$(\ce{I}$_{0.77}$\ce{Br}$_{0.23}$)$_{3}$ onto various substrates. Here, MA stands for Methylammonium and FA stands for Formamidinium. The substrates onto which these solutions were coated include glass, which is amorphous, and $\ce{GaAs}$ wafers, which are single crystalline. Other substrates were stacks of glass/indium tin oxide, stacks of \ce{GaAs}/CIGS, and stacks of glass/CIGS. Here, CIGS stands for a stack of \ce{Mo}, \ce{Cu}(\ce{In}, \ce{Ga})\ce{Se2},\ce{Cds} and \ce{ZnO}. Some of the substrates were additionally covered with a self-assembling monolayer of MeO-2PACz. The $\ce{GaAs}$ substrates were prepared by Dr. Jiro Nishinaga from the National Institute of Advanced Industrial Science and Technology (AIST) in Japan and the glass/CIGS substrates by Dr. Christian Kaufmann and his team at Helmholtz-Zentrum Berlin (HZB) in Germany. Data collection was performed in situ during thin-film deposition using a custom-made spin-coating and annealing stage. \\

@@

For these two datasets, experimental XRD data were collected at beamline 12.3.2 of the Advanced Light Source, the synchrotron at Lawrence Berkeley National Laboratory. The data were collected using a photon energy of 10 $\si{keV}$ ($\lambda = 1.23984 \text{\AA}$), selected using a Si(111) monochromator. Measurements were taken in grazing incidence geometry, i.e. using a beam incidence angle of $1\degree$. Two-dimensional diffraction images were recorded using a Dectris Pilatus 1M area detector at an angle between $34\degree$ and $36\degree$ with a sample-to-detector distance of roughly $190 \ \si{mm}$. The two-dimensional data were calibrated using an Al$_{2}$O$_{3}$ calibration standard and integrated along the azimuthal angle. \\

@@

A third dataset was collected by observing the phase evolution of an Mn-Sb-O system with varying annealing temperatures. The temperatures used to analyze the crystal structure of the Mn-Sb-O system were chosen depending on the number of phase transitions appearing for a certain temperature range. Few changes in the crystal structure appear between room temperature and 300$\degree$C and phase transitions appeared from 300$\degree$C until 850$\degree$C. No phase transition appeared when cooling down. Therefore, the crystal structure was measured every 100$\degree$C between room temperature and 300$\degree$C; every 50$\degree$C between 300$\degree$C and 850$\degree$C; and every 200$\degree$C when cooling down. The heating and cooling rates are fixed for all the experiments at 50$\degree$C/min and the holding time is fixed at 2 min. \\

### 2024-12-22 main.tex
Added alphabetic labeling rule in Usage section

\subsection*{Supporting Information}
Supporting Information is available from the Wiley Online Library or the author.

>>>>

\pagebreak

\subsection*{Supporting Information}
%Supporting Information is available from the Wiley Online Library or the author.

The below figure $\eqref{fig:combined}$ displays a randomly selected sample of the X-ray diffraction patterns found in each of the research projects contributed to the opXRD database.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth]{figures/combined.png}
    \caption{50 randomly chosen X-ray diffraction patterns from each contributed dataset. The figure shows data from the following datasets: a) EMPA, b) LBNL-A, c) LBNL-B, d) LBNL-C, e) USC, f) INT, g) HKUST-A, h) HKUST-B, i) CNRS, j) IKFT.}
    \label{fig:combined}
\end{figure}

\pagebreak
